Sweep A - general experiment analysis.

### 2018-04-03 voltagebudget/analysis/freq_analysis.Rmd
Improved freq vis

# --------------------------
exp <- "77"
freqs <- c(24, 30)

@@

# --------------------------
exp <- "79"
freqs <- c(6, 8, 10, 12, 14, 16, 18, 20)

@@

@@

results %>% 
  group_by(As, freq) %>% 
  summarise(
    V_osc = mean(V_osc),
    delta_spikes = mean(delta_spikes),
    V_comp = mean(V_comp), 
    errors = mean(errors), 
    variances = mean(variances)) -> avg_results

@@

- WTF? Vo is gettin way to big here...

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  ggplot(aes(x=V_osc*1e3, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x="V_osc (mvolt)", y="Spike count") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  ggplot(aes(x=V_osc*1e3, y=errors, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x="V_osc (mvolt)", y="Error (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.3, fig.height=0.8}
avg_results %>% 
  ggplot(aes(x=V_osc*1e3, y=variances, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x="V_osc (mvolt)", y="Variance (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.2, fig.height=0.8}
results %>%
  filter(rank == 0) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.2) + 
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) 
```

>>>>

# --------------------------
# exp <- "77"
exp <- "96"
freqs <- c(24, 30, 40)

@@

# --------------------------
# exp <- "79"
exp <- "94"
freqs <- c(6, 8, 10, 12, 14, 16, 18, 20)

@@

# exp <- "80"
exp <- "95"
freqs <- c(22, 24, 26, 28, 32, 34 ,36, 38)
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

@@

results %>% 
  group_by(As, freq) %>% 
  summarise(
    N = 0,
    V_b = mean(V_b),
    V_osc = mean(V_osc),
    delta_spikes = mean(delta_spikes),
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    V_comp = mean(V_comp), 
    errors = mean(errors), 
    variances_pop = mean(variances_pop),
    variances = mean(variances)) -> avg_results

@@

```{r, fig.width=1.2, fig.height=0.8}
results %>%
  filter(N == 0) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=As*1e9, y=errors_pop*1e3, color=freq, group=interaction(N, freq))) +
  # geom_point(size=0.4, alpha=0.5) + 
  geom_line(size=0.5, alpha=0.5) + 
  labs(x="As (namp)", y="Error (ms)") +
  theme_classic() +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) 
```

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>%
  filter(As < 0.05e-9) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=As*1e9, y=variances_pop*1e3, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.5, alpha=0.5) + 
  labs(x="As (namp)", y="Variance (ms)") +
  theme_classic() +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) 
```

### V_osc/V_comp

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors_pop*1e3, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  labs(x="V_osc/V_comp", y="Error (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*1e3, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  labs(x="V_osc/V_comp", y="Variance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
  theme_classic() +
  lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.5, alpha=0.5) + 
  labs(x="V_osc/V_comp", y="Avg. count") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```
